Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-03-07 main_paper.tex
Tweak reference to CCT's notation

This section provides additional details of RD estimators in general and of
CCT's proposed bias correction. It also defines some of the notation and
presents the assumptions that will be used for our theoretical analysis in
Section~\ref{boot}.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation (largely
introduced by CCT): $r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
\end{align*}
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

>>>>

This section provides additional details of RD estimators in general and of
CCT's proposed bias correction. It also defines some of the notation and
presents the assumptions that will be used for our theoretical analysis in
Section~\ref{boot}. We have adopted CCT's notation where possible to aid
readers familiar with that paper.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
\end{align*}
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}
